Methodology for Assessing the State of the Practice for Domain X

### 2020-10-23 StateOfPractice/Methodology/Methodology.tex
added some notes into Section 9 Measure Using Measurment Template regarding ambiguities of measurement tamplate

>>>>

\pmi{first pass for `tricky parts'; under summary information:
	``Publications about the software''
	list of publications can be found on some software websites, for others you may use google scholar or similar indexes,
	``Is there evidence that performance was considered?''	Look for mention of any items, broad scope to answer yes but must include explanatory text: speed, storage, throughput consideration as well as comments on performance optimization/development, GPU processing, parallelism, multicore processing, or similar considerations}
